### 2018-09-28 README.Rmd
rebuild docs
clean up
lighter dependencies, cleaner flow.
refactor
- no default disk location
- td_home() sets home location
- file names by function name
- more portable an consistent fn names
progress to simplifying and abstracting db connection

Before we can use most `taxald` functions, we need to do a one-time installation of the database `taxald` uses for almost all commands.  This can take a while to run, but needs only be done once.  The database is installed on your local harddisk and will persist between R sessions.  Download and install the database like so:

```{r eval = TRUE, message=FALSE}
tic()
create_taxadb()
toc()
```

The default behavior installs only the ITIS database using the hierachy schema.  While this should be sufficient for getting started on basic tasks like looking up classification or translating between IDs and scientific names, users will want to install additional authorities and schemas for advanced use. See the `authorities` vignette for details.  By default, `taxald` will install the database into a hidden `.taxald` folder in your home directory (`~/.taxald`).  You can control this by passing the path to `create_taxadb()` or setting the environmental variable `TAXALD_HOME` to a different location.

>>>>

Before we can use most `taxald` functions, we need to do a one-time installation of the database `taxald` uses for almost all commands.  This can take a while to run, but needs only be done once.  The database is installed on your local harddisk and will persist between R sessions.  By default, the database will be installed in your user's application data directory, as detected by the `rappdirs` package.  (Set a custom location instead using `dbdir` argument.)

```{r }
td_create()
```

The default behavior installs only the ITIS database.  While this should be sufficient for getting started on basic tasks like looking up classification or translating between IDs and scientific names, users will want to install additional authorities and schemas for advanced use. See the `authorities` vignette for details.  By default, `taxald` will install the database into a hidden `.taxald` folder in your home directory (`~/.taxald`).  You can control this by passing the path to `create_taxadb()` or setting the environmental variable `TAXALD_HOME` to a different location.
